\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-29 Papers/ViscousInstabilities/article_figure1.tex
do not rush Kostas

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{4.0cm}
\includegraphics[width=.8\textwidth]{./Pics/map_of_boundaries.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) map of permeabilties K   
}
\vspace{0.25cm}
\hbox{\hspace{4.0cm}
\includegraphics[width=.8\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{9cm} (b)      
}
}     
\caption{(a) describes the initial and boundary conditions as these are applied in this set of simulations. Below (b) the unstructured and fixed mesh can been seen and there is a colored representation of permeabilities.}
\label{fig:testcase_heter_domain}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=250 (fixed mesh)  
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=250 (adaptive mesh)    
}
}     
\caption{Start to compare $2$ test-cases under MR=$10$ and under fixed (top) and adaptive(bottom) mesh for $time=0.125$ sec ($t=250$, timestemp). There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=500 (adaptive mesh)     
}
}     
\caption{At $time=0.25sec$ ($t=500$, timestemp) cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound for for the (b) case below.}
\label{fig:2testcase_b}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=1500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=1500 (adaptive mesh)     
}
}     
\caption{At $time=0.75 sec$ ($t=1500$, timestemp) cross flow at the upper part has almost travel all the way towards the outlet (left-hand side) and the finger below start forming a front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe. The end of simulation happens at $time=5 sec$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{4.0cm}
\includegraphics[width=.8\textwidth]{./Pics/map_of_boundaries.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) map of permeabilties K   
}
\vspace{0.25cm}
\hbox{\hspace{4.0cm}
\includegraphics[width=.8\textwidth]{./Pics/4r_po_adapt_fine_125_mesh.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{9cm} (b)      
}
}     
\caption{Figure (a) describes the initial and boundary conditions as these are applied in this set of simulations. Below (b) there is a comparison between the unstructured and fixed mesh and the unstructured and adaptive mesh. During the implementation of fixed mesh initially there $4606$ elements while for the adaptive mesh there are $606$ while the majority of them is on the interface between between the two fluids. }
\label{fig:testcase_heter_domain}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_250.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=250 (fixed mesh)  
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.8\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_250.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=250 (adaptive mesh)    
}
}     
\caption{For $t=0.125$s, $2$ test-cases under the MR=$10$ and under fixed (top) and adaptive(bottom) mesh are compared. There is a significant difference on the main front (left hand side of the domain) and the number of finger that appear.}
\label{fig:2testcase_a}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_500_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=500 (adaptive mesh)     
}
}     
\caption{At $t=0.25$s ($t=500$, timestemp) cross flow is taking place at the upper part of the formation. The fingers start to becoming more proufound as can been seen at the bottom.}
\label{fig:2testcase_b}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_1500.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=1500 (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_1500_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=1500 (adaptive mesh)     
}
}     
\caption{At $t=0.75 sec$ ($t=1500$, timestemp) the initial cross flow is now fully developed and has travel all the way towards the outlet (right-hand side). and the finger below start forming a front that is also travelling towards the left-hand side.}
\label{fig:2testcase_c}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{
\hbox{\hspace{3.5cm}
\includegraphics[width=.65\textwidth]{./Pics1/mr10_5regions_fixed/5regions_fixed_2000.pdf} 
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (a) flow at t=end (fixed mesh)   
}
\vspace{0.25cm}
\hbox{\hspace{3.5cm}
\includegraphics[width=.9\textwidth]{./Pics1/mr10_5regions_adapt/5regions_adapt_3000_1.pdf}
}
\vspace{0.0cm}
\hbox{\hspace{6.5cm} (b) flow at t=end (adaptive mesh)     
}
}     
\caption{Using the $P_{1}DGP_{2}$ element type for MR=$10$ under the same time steps, we compared the impact of fixed and adaptive mesh for the same timeframe. The end of simulation happens at $time=5 sec$ and for the timestemp $t=9999$ while the number of elements in both simulations was approximately $4700$. When adaptive mesh is introduce there is better repersentation of the fluid instabilities as these are developed on time.}
\label{fig:2testcase_d}
\end{figure}
\end{landscape}
\clearpage
